%!TEX root = proposal.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[sigconf]{acmart}
\settopmatter{printacmref=false}
\renewcommand\footnotetextcopyrightpermission[1]{}
\usepackage{enumitem}

% Copyright
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

%Conference
\acmConference[Proposal for Bachelorthesis ]{SEEMOO }{Juni 2025}{Darmstadt, Germany} 
% \acmYear{2018}
% \copyrightyear{2018}
% \acmArticle{4}
% \acmPrice{15.00}

\begin{document}
\title{ATAK Plugin for Decentralized Communication via FutureSDR}

% Comment out the following for you final document
%\subtitle{One-page Summary}

\author{Junchi Weng}
\affiliation{%
  \institution{Technische Universit\"at Darmstadt}
}
\email{junchi.weng@stud.tu-darmstadt.de}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{J.Weng}

\begin{comment}
  \begin{abstract} % do not use this section in the one-page summary
    You may want to answer the following questions with roughly one sentence each.

    \begin{itemize}
    \item What is the topic of your main seminar paper?
    \item What problem does it solve?
    \item Why is that topic/problem important?
    \item What methodologies do the authors apply?
    \item What are the main contributions of the paper?
    \item What are the key findings/results of the paper?
    \end{itemize}
    
  \textbf{Hint 1:} You do not have to answer every question above. Consider only those that are relevant to your paper. 

  \end{abstract}
  ......
\end{comment}


\maketitle

\input{Motivation/motivation.tex}


\input{Related_Work/related_work.tex}



\section{Relevant Section}
Main content starts here. \nocite{*} \\
Structure it well. You can create as many sections and subsections as necessary (but do not overuse this).

\section{Conclusion}
The conclusion goes here.\\

% Remove this note when submitting your report
\textbf{Hint 2:} For the final paper, you are expected to use this template. In addition, to the research questions you answered in the one page-summary, you may want to consider the following ones in your final seminar paper.
  \begin{itemize}
  \item What is your research question?
  \item Why are that question and your topic important?
  \item How did you proceed to answer the question?
  \item What (do you think) is the answer to your question?
  \item Give an overall opinion on your topic.
  \item If you have results, describe them.
  \item What is the impact of the answers to your questions?
  \end{itemize}
  
\textbf{Note 3:} Examples for the final paper are also provided in Moodle. Again, these examples are only referential and you are not expected to mimic their structure. 


% References
\newpage
\bibliographystyle{ACM-Reference-Format}
\bibliography{library} 

\end{document}
